---
title: "Homework 1"
author: "Jingyu Fu"
date: "2019/9/17"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# problem 1

## problem 1.1
```{r}
library(tidyverse)

prob1_df = tibble(
  df_sample = rnorm(8),
  vec_logical = df_sample > 0,
  vec_char = c("today","is","monday","and","8","pm","in","hammer"),
  vec_factor = c("1","1","2","2", "3","3","3","3")
)

mean(pull(prob1_df, df_sample))
mean(pull(prob1_df, vec_logical))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))

```

Taking the mean of df_sample and vec_logical work, but taking the mean of vec_char and vec_factor don't work. 

## problem 1.2
```{r prob1_1, eval = FALSE}
as.numeric(pull(prob1_df, df_sample))
as.numeric(pull(prob1_df, vec_logical))
as.numeric(pull(prob1_df, vec_char))
as.numeric(pull(prob1_df, vec_factor))
```

First of all, converting df_sample into numeric works becuase it contains 8 numeric sample and all you need is just to list out all eight numeric samples. Secondly, converting vec_char into numeric doesn't work because it is not numeric itself, and doesn't contain any information that can be related to numbers. Also, vec_factor is shown as number 1, 2 and 3 becuase factor contains three levels, and converting it to numeric means calculating how many levels this factor contains, and then each factor level stands for a number. Last but importantly, vec_logical is shown as 1 and 0 becuase similar to the converting process of vec_factor, you need to calculate how many different logical results there are and each result resembles a bumber. In this case, logical results contain true and false, and in computer language 0 refers to false and 1 refers to 1, therefore it is shown as 0 and 1 in correspondence with false and true.  

## problem 1.3
```{r prob1_2, eval = FALSE}
as.numeric(pull(prob1_df, vec_logical))*pull(prob1_df, df_sample)
as.factor(pull(prob1_df, vec_logical))*pull(prob1_df, df_sample)
as.numeric(as.factor(pull(prob1_df, vec_logical)))*pull(prob1_df, df_sample)
```

# problem 2

## proble 2.1

```{r}
prob2_df = tibble  (
  x = rnorm (500),
  y = rnorm (500),
  vec_logical_2 = x + y > 1,
  vec_numeric_2 = as.numeric (vec_logical_2 ),
  vec_factor_2 = as.factor (vec_logical_2)
)
  
```

## problem 2.2

The size of the dataset is `r nrow (prob2_df)` rows and `r ncol (prob2_df)` columns. 

The mean of x is `r mean (pull(prob2_df, x))`, the median of x is `r median (pull(prob2_df, x))`, and the standrd deviation of x is `r sd (pull(prob2_df, x))`. 

The proportion of case for which x + y > 1 is `r mean ( pull(prob2_df, vec_numeric_2))`.

## problem 2.3

```{r}
ggplot (prob2_df, aes(x = x, y = y, color= vec_logical_2) ) + geom_point()
ggsave("scatter_plot.pdf", height = 6, width = 6)
ggplot (prob2_df, aes(x = x, y = y, color= vec_numeric_2) ) + geom_point()
ggplot (prob2_df, aes(x = x, y = y, color= vec_factor_2) ) + geom_point()

```

Three scattere plots have similar color scales. All of them range from -1 to 3 on x asix and range from -1 2.5 to on y axis. 








